---
title: "Data Programming"
subtitle: "Homework 1"
author: "Name Surname"
date: "`r format(Sys.time(), '%e %B %Y')`"
format: 
  html:
    embed-resources: true
execute: 
  warning: false
  messages: false
  echo: true
  error: true
---

## Solutions

Submit a **.html** file created using Quarto via e-classroom. A sample is attached. Display all code (packages,input) and output.

Transform the dataframe **automobile**

```{r}
automobile<-mtcars
```

1.  Move rownames to a column **cars.name**, remove rownames.
2.  Add a column named **l/100km** whose values are based on column mpg, then delete column mpg.
3.  Change the **am** column to a factor with levels **Automatic** and **Manual**.

```{r}
# solve 1-3 here




```

After the transformation display the data frame as a tibble then answer these questions independently.

```{r}
#| echo: false
#installs tidyverse and quarto if not done already, delete this chunk after running it once.
normalpackages<-c("tidyverse","quarto")
   new.packages <- normalpackages[!(normalpackages %in% installed.packages()[,"Package"])]
  if(length(new.packages)>0) {install.packages(new.packages,dependencies =T,quiet = T)}
```

```{r}
library(tidyverse)
as.tibble(automobile)
```

4.  What is the average number of gears?
5.  Return the rows with cars with horsepower between 200 and 400.
6.  Which car is most fuel efficient car among 6 cylinder cars?

```{r}
# solve 4-6 here




```
